Large Scale Structure Reconstruction with Short-Wavelength Modes

### 2019-10-08 paper/v1.tex
1

\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\bea{\begin{eqnarray}}
\def\eea{\end{eqnarray}}
\newcommand{\vs}{\nonumber\\}
\newcommand{\vk}{\vec{k}}
\newcommand{\ec}[1]{Eq.~(\ref{eq:#1})}
\newcommand{\eec}[2]{Eqs.~(\ref{eq:#1}) and (\ref{eq:#2})}
\newcommand{\Ec}[1]{(\ref{eq:#1})}
\newcommand{\eql}[1]{\label{eq:#1}}
\newcommand{\rf}[1]{\ref{fig:#1}}
\newcommand{\sfig}[2]{
\includegraphics[width=#2]{../plots/#1}
        }
\newcommand{\sfigg}[2]{
\includegraphics[width=0.45\paperwidth]{../plots/#1}
        }
\newcommand{\sfigr}[2]{
\includegraphics[angle=270,origin=c,width=#2]{#1}
        }
\newcommand{\sfigra}[2]{
\includegraphics[angle=90,origin=c,width=#2]{#1}
        }
\newcommand{\Sfig}[2]{
   \begin{figure}[thbp]
   \begin{center}
    \sfig{../plots/#1.pdf}{\columnwidth}
    \caption{{\small #2}}
    \label{fig:#1}
     \end{center}
   \end{figure}
}
\newcommand{\Sfigg}[2]{
   \begin{figure}[thbp]
    \sfigg{../plots/#1.pdf}{\columnwidth}
    \caption{{\small #2}}
    \label{fig:#1}
   \end{figure}
}
\newcommand{\Spng}[2]{
   \begin{figure}[thbp]
   \begin{center}
    \sfigg{../plots/#1.png}{\columnwidth}
    \caption{{\small #2}}
    \label{fig:#1}
     \end{center}
   \end{figure}
}

@@

\date{\today}
\begin{abstract}
\noindent Large scale density modes cannot be measured directly through surveys but we can study them by measuring perturbations on small scales. Cosmological perturbation theory predicts that second-order density inhomogeneities can be considered as convolution of a short- and long-wavelength mode. This arises physically because small structure structure varies depending on the large scale environment in which it resides. And this will induce an off-diagonal term of two-point density correlations, from which we can build a quadratic estimator with the same form as CMB lensing estimator. We tested the robustness of the theory using data from large cosmological N-body simulation. We checked the accuracy of large scale density modes from this quadratic estimator and discussed signal-to-noise and potential bias of the theory.

\end{abstract}
\maketitle
\section{Introduction}
Measuring large scale structures of order $10^3\, \rm Mpc$ has been one of the main goals of recent surveys despite it is extremely difficult to get a direct detection. To tackle this problem, relations between long- and short-wavelength modes have been frequently discussed recent years \cite{Baldauf:2011fer}\cite{Barreira:2017res}. Method of using small scale position-dependent power spectrum to compute squeezed-limit bispectrum also indicates that we can use small scale perturbation to infer large scale information to some extent \cite{Chiang:2014pos}\cite{Chiang:2015poss}. In order to fully accomplish this goal, we develop in this work a generalized approach of building a quadratic estimator for long-wavelength modes. \\
Starting from second-order SPT\footnote{SPT stands for standard perturbation theory.} \cite{Goroff:1986sts}\cite{Makino:1992fs}\cite{Jain:1994sop}, we can identify the second-order correction of a short-wavelength mode as a convolution of a short- and long-wavelength mode. This can be further related to CMB lensing case \cite{Hu:2002mr}, where CMB temperature field has a second-order correction due to gravitational field along line of sight. Similarly in this case the short-wavelength mode's nonlinear terms are related to the large scale environment it belongs to.
\\
Inspired by CMB lensing quadratic estimator's construction, where small scale temperature correlation functions have off-diagonal terms due to
large scale perturbations caused by gravitational lensing. The same procedure applies in our case as well - off-diagonal terms of small scale correlations are no-longer zero due to large scale modes. Thus we can create quadratic estimator for long-wavelength modes using exact same routine. \\
We begin with a brief review of standard perturbation theory and its detailed formalism up to second-order in section \ref{sec1}. Then we build the quadratic estimator and compute signal-to-noise of the estimator in section \ref{sec2}. In \ref{sec3} we present a concise study of the estimator with data from N-body simulation. Finally we conclude this work and discuss future work related to this in section \ref{sec4}. We use flat $\Lambda$CDM model with Planck Collaboration XVI (2014) \cite{Planck:2014cos} cosmological parameters in this work (same as parameters of the N-body simulation).

@@

In this section we review the SPT approach which describes small scale nonlinearity. In the case of a perfect pressurelesee fluid, the nonrelativistic cosmological fluid equations are continuity, Euler and Poisson equations:

@@

\frac{\partial \delta(\vec{x},\tau)}{\partial \tau} &+&\vec{\nabla}\times [(1+\delta(\vec{x},\tau))\vec{v}(\vec{x},\tau)] =0 \\

@@

&&\nabla^2 \Phi = 4\pi G a^2 \bar{\rho}_{\rm m} \delta(\vec{x},\tau) 

@@

these equations fully determine the time evolution of the local density contrast $\delta$ and the peculiar velocity field $\vec{v}=d\vec{x}/d\tau$. Taking the divergence of \ec{eulereq} we can eliminate the gravitational potential $\Phi$ in Fourier space and get evolution equations for $\delta(\vk,\tau)$ and $\theta(\vk,\tau)$ in Fourier space:

@@

\frac{\partial{\delta}}{\partial\tau} + {\theta} &=& -\int \frac{d^{3}\vk_{1}}{(2\pi)^3} \int \frac{d^{3}\vk_{2}}{(2\pi)^3} (2\pi)^3 \delta_{\rm D}(\vk-\vk_{12}) \vs
&& \times\frac{\vk \cdot \vk_1}{k_1^2}{\theta}(\vk_1,\tau){\delta}(\vk_2,\tau) \eql{fouriercont}\\
\frac{\partial{\delta}}{\partial\tau}+\frac{da}{d\tau}\frac{{\theta}}{a}+\frac{6}{\tau^2}{\delta}&=&-\int \frac{d^{3}\vk_{1}}{(2\pi)^3} \int \frac{d^{3}\vk_{2}}{(2\pi)^3} (2\pi)^3 \delta_{\rm D}(\vk-\vk_{12})\vs
&&\times \frac{k^2(\vk_1 \cdot \vk_2)}{2k_1^2 k_2^2} {\theta}(\vk_1,\tau){\theta}(\vk_2,\tau) \eql{fouriereuler}

@@

here $\vk_{12}=\vk_1 +\vk_2$ and more generally $\vk_{1\cdots n}=\vk_1 + \cdots +\vk_n$; $\theta\equiv \vec{\nabla}\cdot \vec{v}$ is the divergence of velocity field.\\
In Einstein-de Sitter space, linear growth function $D_{1}(a)=a$ and we can solve these equations perturbatively using expansion:
{\delta}(\vk,\tau)&=&\sum_{n=1}^{\infty} {\delta}^{(n)}(\vk,\tau)=\sum_{n=1}^{\infty}a^{n}(\tau)\delta_{n}(\vk) \\ {\theta}(\vk,\tau)&=&\sum_{n=1}^{\infty}{\theta}^{(n)}(\vk,\tau)=-H(\tau)\sum_{n=1}^{\infty}a^{n+1}(\tau)\theta_{n}(\vk) 
\\where the superscript $(n)$ means the order of perturbation theory, and first order term ${\delta}^{(1)}$ corresponds to linear evolution. Linear power spectrum is given by this first order term via:

@@

\langle {\delta}(\vk){\delta}(\vk') \rangle =(2\pi)^3 \delta_{\rm D}(\vk+\vk')P_{\rm lin}(k) \eql{lin}

@@

Substituting the two perturbative series into \ec{fouriercont} and \ec{fouriereuler} we get recursion relations for ${\delta}_{n}(\vk)$ and ${\theta}_{n}(\vk)$ with solution:
{\delta}_{n}(\vk) &=& \int \frac{d^{3}\vk_{1}}{(2\pi)^3} \cdots \int \frac{d^{3}\vk_{n}}{(2\pi)^3}(2\pi)^3 \delta_{\rm D} (\vk-\vk_{1\cdots n}) \vs
&&\times F_{n}(\vk_1,\cdots,\vk_n){\delta}_1(\vk_{1}) \cdots {\delta}_1(\vk_{n}) \\
{\theta}_{n}(\vk) &=& \int \frac{d^{3}\vk_{1}}{(2\pi)^3} \cdots \int \frac{d^{3}\vk_{n}}{(2\pi)^3}(2\pi)^3 \delta_{\rm D} (\vk-\vk_{1\cdots n}) \vs
&&\times G_{n}(\vk_1,\cdots,\vk_n){\delta}_1(\vk_{1}) \cdots {\delta}_1(\vk_{n})
and recursion relations are encoded in kernels $F_n$ and $G_n$. Since we only consider up to second-order, the second-order symmetrized kernels are given by:
F_{2}(\vk_1,\vk_2)=\frac{5}{7}+\frac{2}{7}\frac{(\vk_1\cdot \vk_2)^2}{k_1^2 k_2^2}+\frac{\vk_1\cdot \vk_2}{2k_1k_2}(\frac{k_1}{k_2}+\frac{k_2}{k_1}) \\
G_{2}(\vk_1,\vk_2)=\frac{3}{7}+\frac{4}{7}\frac{(\vk_1\cdot \vk_2)^2}{k_1^2 k_2^2}+\frac{\vk_1\cdot \vk_2}{2k_1k_2}(\frac{k_1}{k_2}+\frac{k_2}{k_1})
This approach gives a nearly accurate description of $\Lambda$CDM universe \cite{Takahashi:2008to} with slight generalization \cite{Bernardeau:2002rev}:
{\delta}(\vk,\tau) &=&\sum_{n=1}^{\infty} {\delta}^{(n)}(\vk,\tau)=\sum_{n=1}^{\infty}D_1^{n}(\tau)\delta_{n}(\vk) \\
{\theta}(\vk,\tau)&=&\sum_{n=1}^{\infty}{\theta}^{(n)}(\vk,\tau)\vs
&=&-\frac{d\,\ln D_1(\tau)}{d\tau}\sum_{n=1}^{\infty}D_1^{n}(\tau)\theta_{n}(\vk) 
Time-dependent second-order density contrast can be expressed as convolution of two linear density fields with kernel $F_2$:

@@

Second-order SPT gets less accurate higher in the nonlinear regime and will produce a bias of our quadratic estimator, we can see this effect in \ref{sec3}.

\section{Quadratic Estimator}\label{sec2}
For the remainder if the paper, we use subscript $s$ to represent small scale or short-wavelength modes, while $l$ stands for large scale or long-wavelength modes. We also fix $\tau$ at today.\\
Compute the correlation function of two short-wavelength modes $\vk_s$ and $\vk_s'$, in the squeezed limit $\vk_l=\vk_s+\vk_s'$ up to second-order:

@@

We claim that generally correlation function with three Gaussian fields is nonzero under following consideration: if a three-point correlation function consists of two short-wavelength modes and one long-wavelength mode, we can do the following contraction:

@@

We can do this contraction twice in this integral. One occurs when $|\vk| \ll |\vk_s|,\, |\vk_s'-\vk|$, we can extract ${\delta}^{(1)}(\vk)$ out; the other one occurs when $|\vk_s'-\vk| \ll |\vk|,\,|\vk_s|$.\\

@@

\ec{2pt} suggests that we can estimate long-wavelength modes with appropriate average over pairs of shart-wavelength modes. General form of the quadratic estimator can be written as:
\begin{eqnarray}
\hat{\delta}^{(1)}(\vec{k}_l)=A(\vec{k}_l)\int \frac{d^3 \vec{k}_s}{(2\pi)^3} g(\vec{k}_s,\vec{k}_s'){\delta}(\vec{k}_s){\delta}(\vec{k}_s') \eql{quadest}
\end{eqnarray} 
with $g$ being weighting function, $\vk_s'=\vk_l-\vk_s$ and $A$ is defined via $\langle \hat{\delta}^{(1)}(\vec{k}_l) \rangle={\delta}^{(1)}(\vec{k}_l)$:
\begin{eqnarray}
A(\vec{k}_l)=\bigg[\int \frac{d^3 \vec{k}_s}{(2\pi)^3} g(\vec{k}_s,\vec{k}_s')f(\vec{k}_s,\vec{k}_s')  \bigg]^{-1}
\end{eqnarray}
The Gaussian noise is given by:
\langle \hat{\delta}^{(1)}(\vk_{l})\hat{\delta}^{(1)}(\vk_{l}') \rangle = (2\pi)^3 \delta_{\rm D}(\vk_{l}-\vk_{l}')[P_{\rm lin}(k_{l})+N(\vk_l)]
\begin{eqnarray}
&&N(\vec{k}_{l})=2A^2(\vk_{l})\vs
&&\times\int \frac{d^3 \vec{k}_{s}}{(2\pi)^3} g^2(\vec{k}_{s},\vk_l-\vec{k}_{s})P_{\rm nl}(k_{s})P_{\rm nl}(|\vk_l-\vk_s|)
\end{eqnarray}
where $P_{\rm nl}$ is the nonlinear power spectrum. Minimizing the noise term we can fix the form of $g$ to be:
\begin{eqnarray}
g(\vec{k}_{s},\vec{k}_{s}')=\frac{f(\vec{k}_{s},\vec{k}_{s}')}{2P_{\rm nl}(k_{s})P_{\rm nl}(k_{s}')}
\end{eqnarray} 
Noise term reduces simply to $N(\vk_l)=A(\vk_l)$.\\
\Sfig{SN}{Detectability of long-wavelength modes. We assume a toy survey of boxsize $8.85\, \rm Gpc$.}

\section{N-Body Simulation}\label{sec3}
We test the power of the quadratic estimator using data from snapshot at $z=0$ of BigMPDL, one of the MultiDark cosmological simulations \cite{Klypin:2014nov}. Boxsize of BigMDPL is $3.7\,\rm Gpc$. We use dark matter particle data to produce matter inhomogeneities. Galaxy bias should be considered if we use galaxy catalog.\\
We use nbodykit code to get Fourier density modes \cite{Hand:2018nby} and compare $\delta(\vk_l)$ with $\hat{\delta}(\vk_l)$ in Fig.~\rf{hist}. $\delta(\vk_l)$ is the long-wavelength modes we get directly from N-body simulation and $\hat{\delta}(\vk_l)$ is the reproduced modes using quadratic estimator \ec{quadest}.\\
\Sfig{hist}{Histogram of number counts of $|\hat{\delta}(\vk_l)/\delta(\vk_l)|$ in Fourier space with different integration range of $k_s$. We can see that in the weakly nonlinear regime, left plot peaks at $1$ which is what we would expect. While for the right plot, when we go higher into nonlinear scale, ratio peak at about $1.3$. This bias comes from the inaccuracy of second-order perturbation theory.}

>>>>

\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\bea{\begin{eqnarray}}
\def\eea{\end{eqnarray}}
\newcommand{\vs}{\nonumber\\}
\newcommand{\vk}{\vec{k}}
\newcommand{\ec}[1]{Eq.~(\ref{eq:#1})}
\newcommand{\eec}[2]{Eqs.~(\ref{eq:#1}) and (\ref{eq:#2})}
\newcommand{\Ec}[1]{(\ref{eq:#1})}
\newcommand{\eql}[1]{\label{eq:#1}}
\newcommand{\rf}[1]{\ref{fig:#1}}
\newcommand{\sfig}[2]{
\includegraphics[width=#2]{../plots/#1}
        }
\newcommand{\sfigg}[2]{
\includegraphics[width=0.9\paperwidth]{../plots/#1}
        }
\newcommand{\sfigr}[2]{
\includegraphics[angle=270,origin=c,width=#2]{#1}
        }
\newcommand{\sfigra}[2]{
\includegraphics[angle=90,origin=c,width=#2]{#1}
        }
\newcommand{\Sfig}[2]{
   \begin{figure}[thbp]
   \begin{center}
    \sfig{../plots/#1.pdf}{\columnwidth}
    \caption{{\small #2}}
    \label{fig:#1}
     \end{center}
   \end{figure}
}
\newcommand{\Sfigg}[2]{
   \begin{figure*}[thbp]
    \sfigg{../plots/#1.pdf}{\columnwidth}
    \caption{{\small #2}}
    \label{fig:#1}
   \end{figure*}
}
\newcommand{\Spng}[2]{
   \begin{figure}[thbp]
   \begin{center}
    \sfigg{../plots/#1.png}{\columnwidth}
    \caption{{\small #2}}
    \label{fig:#1}
     \end{center}
   \end{figure}
}

@@

\date{\today}
\begin{abstract}
\noindent Large scale density modes cannot be measured directly through surveys but we can study them by measuring perturbations on small scales. Cosmological perturbation theory predicts that second-order density inhomogeneities are a convolution of a short- and a long-wavelength mode. This arises physically because small structure structure varies depending on the large scale environment in which it resides. This will induce position-dependent clustering in real space and an off-diagonal term in two-point statistics in Fourier space. Therefore we can build a quadratic estimator for the large scale field. We demonstrate that this quadratic estimator works amazingly well for our N-body simulation test.

\end{abstract}
\maketitle
\section{Introduction}
Measuring the distribution of structures on large scales has been one of the main goals of recent surveys despite it is hard to accomplish directly. To tackle this problem, relations between long- and short-wavelength modes have been frequently discussed recent years \cite{Baldauf:2011fer}\cite{Barreira:2017res}. Method of using small scale position-dependent power spectrum to compute squeezed-limit bispectrum also indicates that we can use small scale perturbation to infer large scale information to some extent \cite{Chiang:2014pos}\cite{Chiang:2015poss}. In order to achieve this goal, we develop in this work a generalized approach of building a quadratic estimator to measure long-wavelength modes indirectly. \\
Starting from second-order standard perturbation theory (SPT) \cite{Goroff:1986sts}\cite{Makino:1992fs}\cite{Jain:1994sop}, we can identify second-order perturbation of a short-wavelength mode as a convolution of a short- and a long-wavelength mode. This can be further related to cosmic microwave background (CMB) lensing case \cite{Hu:2002mr}, where CMB temperature field has a second-order correction due to gravitational field along line of sight. Similarly in this case the short-wavelength mode's nonlinear terms are related to the large scale environment it belongs to.
\\
During CMB lensing quadratic estimator's construction, small scale two-point correlation of CMB temperature modes has off-diagonal terms due to large scale perturbations caused by gravitational lensing. The same procedure applies in our case as well - off-diagonal terms of small scale correlations are no-longer zero due to large scale modes. Thus we can create a quadratic estimator for long-wavelength modes using the exact same formalism. \\
We begin with a brief review of SPT up to second-order in section \ref{sec1}. Then we build the quadratic estimator and compute the detectability of the estimator in section \ref{sec2}. In section \ref{sec3} we present a concise study of the estimator with data from N-body simulation. Finally we conclude this work and discuss future work related to this in section \ref{sec4}. We use flat $\Lambda$CDM model with Planck Collaboration XVI (2014) \cite{Planck:2014cos} cosmological parameters in this work (same as parameters of the N-body simulation).

@@

In this section we review the SPT approach which describes small scale nonlinearity. Then we compute the off-diagonal term of two short-wavelength modes in the squeezed limit. This off-diagonal term proportional to \peikai{with or without an "a"?}long-wavelength mode will be the key factor of constructing the quadratic estimator. \\
Starting from a perfect pressureless fluid, the nonrelativistic cosmological fluid equations are continuity, Euler and Poisson equations:

@@

\frac{\partial \delta(\vec{x},\tau)}{\partial \tau} &+&\vec{\nabla}\times [(1+\delta(\vec{x},\tau))\vec{v}(\vec{x},\tau)] =0\eql{fluid1} \\

@@

&&\nabla^2 \Phi = 4\pi G a^2 \bar{\rho}_{\rm m} \delta(\vec{x},\tau) \eql{fluid3}

@@

these equations fully determine the time evolution of the local density contrast $\delta$ and the peculiar velocity field $\vec{v}=d\vec{x}/d\tau$.\\
We can solve these equations in Fourier space with perturbative expansion \cite{Bernardeau:2002rev}:

@@

{\delta}(\vk,\tau) &=&\sum_{n=1}^{\infty} {\delta}^{(n)}(\vk,\tau)=\sum_{n=1}^{\infty}D_1^{n}(\tau)\delta_{n}(\vk)  \eql{pert1}\\
{\theta}(\vk,\tau)&=&\sum_{n=1}^{\infty}{\theta}^{(n)}(\vk,\tau) \vs
&=&-\frac{d\,\ln D_1(\tau)}{d\tau}\sum_{n=1}^{\infty}D_1^{n}(\tau)\theta_{n}(\vk) \eql{pert2}

@@

where $D_1$ is the linear growth factor. The first order term ${\delta}^{(1)}$ corresponds to linear evolution. The inear power spectrum is given by this first order term via:

@@

\langle {\delta^{(1)}}(\vk,\tau){\delta^{(1)}}(\vk',\tau) \rangle =(2\pi)^3 \delta_{\rm D}(\vk+\vk')P_{\rm lin}(k,\tau) \eql{lin}

@@

Plugging the perturbative series \ec{pert1} and \ec{pert2} into the fluid equations \ec{fluid1}-\ec{fluid3} after Fourier transform, we can solve second-order density contrast and the result is given by:

@@

F_{2}(\vk_1,\vk_2)=\frac{5}{7}+\frac{2}{7}\frac{(\vk_1\cdot \vk_2)^2}{k_1^2 k_2^2}+\frac{\vk_1\cdot \vk_2}{2k_1k_2}(\frac{k_1}{k_2}+\frac{k_2}{k_1})\eql{f2}
Notice \ec{f2} is derived in Einstein-de Sitter universe. Nonetheless when we actually do relative calculation in $\Lambda$CDM universe, the difference is negligible \cite{Takahashi:2008to} thus we still use the expression from \ec{f2} throughout the whole work.\\
Compute the two-point correlations of two short-wavelength modes $\vk_s$ and $\vk_s'$, in the squeezed limit $\vk_l=\vk_s+\vk_s'$ up to second-order where $\vk_l$ corresponds to a long-wavelength mode we have ($\tau$ is fixed at today):

@@

We claim that generally correlation function of three Gaussian fields is nonzero under following consideration: if a three-point correlation function consists of two short-wavelength modes and one long-wavelength mode, we can do the following contraction:

@@

We can do this contraction twice in this integral \ec{integral}. One occurs when $|\vk| \ll |\vk_s|,\, |\vk_s'-\vk|$, we can extract ${\delta}^{(1)}(\vk)$ out; the other one occurs when $|\vk_s'-\vk| \ll |\vk|,\,|\vk_s|$.\\

@@

\ec{2pt} suggests that we can estimate long-wavelength modes using short-wavelength modes. Also notice that second-order SPT gets less accurate higher in the nonlinear regime and will produce a bias of our quadratic estimator, we can see this effect in \ref{sec3}.

%Taking the divergence of \ec{eulereq} we can eliminate the gravitational potential $\Phi$ in Fourier space and get evolution equations for $\delta(\vk,\tau)$ and $\theta(\vk,\tau)$ in Fourier space:
%\bea 
%\frac{\partial{\delta}}{\partial\tau} + {\theta} &=& -\int \frac{d^{3}\vk_{1}}{(2\pi)^3} \int \frac{d^{3}\vk_{2}}{(2\pi)^3} (2\pi)^3 \delta_{\rm D}(\vk-\vk_{12}) \vs
%&& \times\frac{\vk \cdot \vk_1}{k_1^2}{\theta}(\vk_1,\tau){\delta}(\vk_2,\tau) \eql{fouriercont}\\
%\frac{\partial{\delta}}{\partial\tau}+\frac{da}{d\tau}\frac{{\theta}}{a}+\frac{6}{\tau^2}{\delta}&=&-\int \frac{d^{3}\vk_{1}}{(2\pi)^3} \int \frac{d^{3}\vk_{2}}{(2\pi)^3} (2\pi)^3 \delta_{\rm D}(\vk-\vk_{12})\vs
%&&\times \frac{k^2(\vk_1 \cdot \vk_2)}{2k_1^2 k_2^2} {\theta}(\vk_1,\tau){\theta}(\vk_2,\tau) \eql{fouriereuler}
%\eea
%here $\vk_{12}=\vk_1 +\vk_2$ and more generally $\vk_{1\cdots n}=\vk_1 + \cdots +\vk_n$; $\theta\equiv \vec{\nabla}\cdot \vec{v}$ is the divergence of velocity field.\\
%In Einstein-de Sitter space, linear growth function $D_{1}(a)=a$ and we can solve these equations perturbatively using expansion:
%\bea
%{\delta}(\vk,\tau)&=&\sum_{n=1}^{\infty} {\delta}^{(n)}(\vk,\tau)=\sum_{n=1}^{\infty}a^{n}(\tau)\delta_{n}(\vk) \\ {\theta}(\vk,\tau)&=&\sum_{n=1}^{\infty}{\theta}^{(n)}(\vk,\tau)=-H(\tau)%\sum_{n=1}^{\infty}a^{n+1}(\tau)\theta_{n}(\vk) 
%\eea
%\\where the superscript $(n)$ means the order of perturbation theory, and first order term ${\delta}^{(1)}$ corresponds to linear evolution. Linear power spectrum is given by this first order term via:
%\be 
%\langle {\delta}(\vk){\delta}(\vk') \rangle =(2\pi)^3 \delta_{\rm D}(\vk+\vk')P_{\rm lin}(k) \eql{lin}
%\ee 
%Substituting the two perturbative series into \ec{fouriercont} and \ec{fouriereuler} we get recursion relations for ${\delta}_{n}(\vk)$ and ${\theta}_{n}(\vk)$ with solution:
%\bea
%{\delta}_{n}(\vk) &=& \int \frac{d^{3}\vk_{1}}{(2\pi)^3} \cdots \int \frac{d^{3}\vk_{n}}{(2\pi)^3}(2\pi)^3 \delta_{\rm D} (\vk-\vk_{1\cdots n}) \vs
%&&\times F_{n}(\vk_1,\cdots,\vk_n){\delta}_1(\vk_{1}) \cdots {\delta}_1(\vk_{n}) \\
%{\theta}_{n}(\vk) &=& \int \frac{d^{3}\vk_{1}}{(2\pi)^3} \cdots \int \frac{d^{3}\vk_{n}}{(2\pi)^3}(2\pi)^3 \delta_{\rm D} (\vk-\vk_{1\cdots n}) \vs
%&&\times G_{n}(\vk_1,\cdots,\vk_n){\delta}_1(\vk_{1}) \cdots {\delta}_1(\vk_{n})
%\eea
%and recursion relations are encoded in kernels $F_n$ and $G_n$. Since we only consider up to second-order, the second-order symmetrized kernels are given by:
%\bea 
%F_{2}(\vk_1,\vk_2)=\frac{5}{7}+\frac{2}{7}\frac{(\vk_1\cdot \vk_2)^2}{k_1^2 k_2^2}+\frac{\vk_1\cdot \vk_2}{2k_1k_2}(\frac{k_1}{k_2}+\frac{k_2}{k_1}) \\
%G_{2}(\vk_1,\vk_2)=\frac{3}{7}+\frac{4}{7}\frac{(\vk_1\cdot \vk_2)^2}{k_1^2 k_2^2}+\frac{\vk_1\cdot \vk_2}{2k_1k_2}(\frac{k_1}{k_2}+\frac{k_2}{k_1})
%\eea 
%This approach gives a nearly accurate description of $\Lambda$CDM universe \cite{Takahashi:2008to} with slight generalization \cite{Bernardeau:2002rev}:
%\bea
%{\delta}(\vk,\tau) &=&\sum_{n=1}^{\infty} {\delta}^{(n)}(\vk,\tau)=\sum_{n=1}^{\infty}D_1^{n}(\tau)\delta_{n}(\vk) \\
%{\theta}(\vk,\tau)&=&\sum_{n=1}^{\infty}{\theta}^{(n)}(\vk,\tau)\vs
%&=&-\frac{d\,\ln D_1(\tau)}{d\tau}\sum_{n=1}^{\infty}D_1^{n}(\tau)\theta_{n}(\vk) 
%\eea
%Time-dependent second-order density contrast can be expressed as convolution of two linear density fields with kernel $F_2$:
%\be 
%{\delta}^{(2)}(\vk,\tau)=\int \frac{d^{3}\vk_{1}}{(2\pi)^3} F_2(\vk_1,\vk-\vk_1){\delta}^{(1)}(\vk_1,\tau) {\delta}^{(1)}(\vk-\vk_1,\tau) \eql{sorder}
%\ee

\section{Quadratic Estimator}\label{sec2}
In this section we construct the quadratic estimator for long-wavelength modes starting from \ec{2pt}. Then we forecast the detectability of the quadratic estimator for future surveys. Similar to CMB lensing's construction, we can write the general form of the estimator by averaging over pairs of the short-wavelength modes:
\begin{eqnarray}
\hat{\delta}^{(1)}(\vec{k}_l)=A(\vec{k}_l)\int \frac{d^3 \vec{k}_s}{(2\pi)^3} g(\vec{k}_s,\vec{k}_s'){\delta}(\vec{k}_s){\delta}(\vec{k}_s') \eql{quadest}
\end{eqnarray} 
with $g$ being weighting function, $\vk_s'=\vk_l-\vk_s$ and $A$ is defined via $\langle \hat{\delta}^{(1)}(\vec{k}_l) \rangle={\delta}^{(1)}(\vec{k}_l)$:
\begin{eqnarray}
A(\vec{k}_l)=\bigg[\int \frac{d^3 \vec{k}_s}{(2\pi)^3} g(\vec{k}_s,\vec{k}_s')f(\vec{k}_s,\vec{k}_s')  \bigg]^{-1} \eql{a}
\end{eqnarray}
The Gaussian noise is given by:
\be 
\langle \hat{\delta}^{(1)}(\vk_{l})\hat{\delta}^{(1)}(\vk_{l}') \rangle = (2\pi)^3 \delta_{\rm D}(\vk_{l}-\vk_{l}')[P_{\rm lin}(k_{l})+N(\vk_l)]
\ee 
with 
\begin{eqnarray}
&&N(\vec{k}_{l})=2A^2(\vk_{l})\vs
&&\times\int \frac{d^3 \vec{k}_{s}}{(2\pi)^3} g^2(\vec{k}_{s},\vk_l-\vec{k}_{s})P_{\rm nl}(k_{s})P_{\rm nl}(|\vk_l-\vk_s|)
\end{eqnarray}
where $P_{\rm nl}$ is the nonlinear power spectrum. Minimizing the noise term we can fix the form of $g$ to be:
\begin{eqnarray}
g(\vec{k}_{s},\vec{k}_{s}')=\frac{f(\vec{k}_{s},\vec{k}_{s}')}{2P_{\rm nl}(k_{s})P_{\rm nl}(k_{s}')}
\end{eqnarray} 
Noise term reduces simply to $N(\vk_l)=A(\vk_l)$. We test that the value of $N$ is very insensitive to the choice of the lower limit of the integration \ec{a} since most of the contribution comes from large $k_s$. We will discuss the choice of the upper limit later in section \ref{sec3}.\\
Assuming the noise is Gaussian, the projected detectability of $P(k_l)$ measurement from the quadratic estimator can be expressed as:
\be
\frac{1}{\sigma^{2}(k_l)}=\frac{V k_l^2 \Delta k }{(2\pi)^2}\bigg[\frac{P_{\rm lin}(k_l)}{P_{\rm lin}(k_l)+N(k_l) }\bigg]^2 \eql{error}
\ee
here $V$ is the volume of a survey and we can compute the detectability for a set of narrow $k_l$-bins each separated by width $\Delta k$.
\Sfig{SN}{Long-wavelength power spectrum and its error from \ec{error} which can be expressed as $P(k_l)\sigma(k_l)$. We assume a toy survey of boxsize $L=6\, \rm Gpc$, thus volume $V=L^3$ and width $\Delta k = 2\pi/L$. Moreover, we set the integration range for $\vk_s$ from $0.02 \, \rm Mpc^{-1}$ to $0.15\,\rm Mpc^{-1}$. We will see in the next section \ref{sec3} that this choice of the upper limit of integration is very reasonable for our current construction at $z=0$.}

\section{Demonstration with N-Body Simulation}\label{sec3}
We test the power of the quadratic estimator using data from snapshot at $z=0$ of BigMPDL, one of the MultiDark cosmological simulations \cite{Klypin:2014nov}. Boxsize of BigMDPL is $3.7\,\rm Gpc$. We use dark matter particle data to produce matter inhomogeneities. Galaxy bias should be considered if we use galaxy catalog.\\
We use nbodykit code to get Fourier density modes \cite{Hand:2018nby} and compare $\delta(\vk_l)$ with $\hat{\delta}(\vk_l)$ in Fig.~\rf{hist}. $\delta(\vk_l)$ is the long-wavelength modes we get directly from N-body simulation and $\hat{\delta}(\vk_l)$ is the reproduced modes using quadratic estimator \ec{quadest}.\\
\Sfig{hist}{Histogram of number counts of $|\hat{\delta}(\vk_l)/\delta(\vk_l)|$ in Fourier space with different integration range of $k_s$. We can see that in the weakly nonlinear regime, left plot peaks at $1$ which is what we would expect. While for the right plot, when we go higher into nonlinear scale, ratio peak at about $1.3$. This bias comes from the inaccuracy of second-order perturbation theory.}
